---
title: "Assignment 1: Neural Networks — IMDB Sentiment Classification"
author: "Shivam Shekher"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
    highlight: tango
fontsize: 11pt
geometry: margin=0.9in
header-includes:
  - \usepackage{float}
  - \floatplacement{table}{H}
  - \usepackage{booktabs}
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r knitr-options, include = FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.align  = "center",
  fig.pos    = "H",
  fig.width  = 8,
  fig.height = 5,
  out.width  = "95%"
)
options(knitr.table.format = "latex")
```

# Overview

This report extends the IMDB sentiment-classification network from class. The
baseline is a fully connected network with two hidden layers of 16 ReLU units,
a sigmoid output, RMSprop, and binary crossentropy. Starting from that
baseline, one factor is changed at a time so that every difference in
performance can be attributed to that factor.

| Assignment question | What is changed | Models compared |
|:--|:--|:--|
| 1. Number of hidden layers | 1, 2, 3 hidden layers | 1x16, 2x16, 3x16 |
| 2. Number of hidden units | 8, 16, 32, 64 units per layer | 2x8, 2x16, 2x32, 2x64 |
| 3. Loss function | MSE instead of binary crossentropy | 2x16 BCE vs 2x16 MSE |
| 4. Activation function | tanh instead of ReLU | 16 and 32 units, ReLU vs tanh |
| 5. Improving validation | Dropout, L2 regularization, both | 16, 32 and 64 units |

**Evaluation protocol.** Every model is trained for 20 epochs on 15,000
reviews and monitored on a 10,000-review validation set. For each model the
report records the best validation accuracy and the epoch it occurred at. The
weights from that best epoch are restored and scored on the 25,000-review test
set, so test accuracy reflects the model at its best point rather than after
it has overfit. The final model is chosen on validation accuracy only; the
test set is never used for selection.

# Setup

```{r setup}
library(keras3)
library(dplyr)
library(tidyr)
library(tibble)
library(readr)
library(ggplot2)
library(scales)

SEED              <- 64061L
NUM_WORDS         <- 10000L   # vocabulary size
VALIDATION_N      <- 10000L   # reviews held out for validation
BATCH_SIZE        <- 512L
EXPERIMENT_EPOCHS <- 20L

set.seed(SEED)
dir.create("results", showWarnings = FALSE)
```

# Data

## Loading the IMDB dataset

```{r load-data}
imdb <- dataset_imdb(num_words = NUM_WORDS)

train_data   <- imdb$train$x
train_labels <- as.numeric(imdb$train$y)
test_data    <- imdb$test$x
test_labels  <- as.numeric(imdb$test$y)

cat("Training reviews:", length(train_data), "\n")
cat("Test reviews:    ", length(test_data), "\n")
```

## Preprocessing

Each review is a sequence of word indices. It is converted into a multi-hot
vector of length 10,000, where position *j* is 1 if word *j* appears in the
review. The first 10,000 training reviews form the validation set and the
remaining 15,000 are used for training during the experiments.

**Memory.** Stored as ordinary R numbers (8 bytes each), the four matrices
would take about 6 GB, and each call to `fit()` would convert them into new
Python arrays again. To avoid that, the matrices are built once, directly as
32-bit NumPy arrays (about 2 GB in total). The validation and training splits
are views of the full training array, not copies, and the same arrays are
reused by every model.

```{r preprocessing}
# Small Python helpers: build a multi-hot matrix and split rows without copying
reticulate::py_run_string("
import numpy as np

def multi_hot(rows, cols, n_rows, dim):
    x = np.zeros((int(n_rows), int(dim)), dtype='float32')
    x[np.asarray(rows, dtype='int64'), np.asarray(cols, dtype='int64')] = 1.0
    return x

def head_rows(x, n):
    return x[:int(n)]

def tail_rows(x, n):
    return x[int(n):]
")
py_main <- reticulate::import_main(convert = FALSE)  # keep results in Python

vectorize_sequences <- function(sequences, dimension = NUM_WORDS) {
  rows <- rep(seq_along(sequences) - 1L, lengths(sequences))  # 0-based rows
  cols <- unlist(sequences, use.names = FALSE) - 1L          # word j -> col j-1
  keep <- cols >= 0L & cols < dimension
  py_main$multi_hot(rows[keep], cols[keep], length(sequences), dimension)
}

x_train_full <- vectorize_sequences(train_data)
x_test       <- vectorize_sequences(test_data)
y_train_full <- train_labels
y_test       <- test_labels

x_val           <- py_main$head_rows(x_train_full, VALIDATION_N)
partial_x_train <- py_main$tail_rows(x_train_full, VALIDATION_N)
val_idx         <- seq_len(VALIDATION_N)
y_val           <- y_train_full[val_idx]
partial_y_train <- y_train_full[-val_idx]

rm(imdb, train_data, test_data)
invisible(gc())

print(x_train_full$shape)
print(x_test$shape)
```

## Dataset summary

```{r dataset-summary}
dataset_summary <- tibble(
  Split           = c("Training", "Validation", "Test"),
  Reviews         = c(length(partial_y_train), length(y_val), length(y_test)),
  Features        = NUM_WORDS,
  `Positive rate` = c(mean(partial_y_train), mean(y_val), mean(y_test))
)
write_csv(dataset_summary, "results/dataset_summary.csv")

dataset_summary |>
  mutate(`Positive rate` = percent(`Positive rate`, accuracy = 0.1)) |>
  knitr::kable(caption = "Size and class balance of each split",
               booktabs = TRUE, format.args = list(big.mark = ","))
```

All three splits are close to 50% positive, so accuracy is a fair metric and
a model that always predicts one class would score about 50%.

# Model and Experiment Functions

## Model builder

`build_imdb_model()` builds the class architecture and exposes each factor
the assignment asks about as an argument. When dropout is used, a dropout
layer follows every hidden layer; when L2 is used, it is applied to every
hidden layer's weights.

```{r model-function}
build_imdb_model <- function(hidden_layers = 2L,
                             units         = 16L,
                             activation    = "relu",
                             loss_function = "binary_crossentropy",
                             dropout_rate  = 0,
                             l2            = 0) {
  model <- keras_model_sequential(input_shape = NUM_WORDS)

  for (i in seq_len(hidden_layers)) {
    model <- model |>
      layer_dense(
        units              = units,
        activation         = activation,
        kernel_regularizer = if (l2 > 0) regularizer_l2(l2) else NULL
      )
    if (dropout_rate > 0) {
      model <- model |> layer_dropout(rate = dropout_rate)
    }
  }

  model <- model |> layer_dense(units = 1, activation = "sigmoid")

  model |> compile(
    optimizer = optimizer_rmsprop(),
    loss      = loss_function,
    metrics   = "accuracy"
  )
  model
}
```

## Experiment runner

`run_experiment()` trains one configuration and returns its per-epoch history
and a one-row summary. A checkpoint callback saves the weights from the epoch
with the highest validation accuracy, and those weights are restored before
the test-set evaluation.

```{r experiment-function}
run_experiment <- function(id, label, group, hidden_layers, units,
                           activation, loss_function, dropout_rate, l2) {
  set_random_seed(SEED)   # same initial conditions for every model

  model <- build_imdb_model(hidden_layers, units, activation,
                            loss_function, dropout_rate, l2)

  checkpoint_path <- file.path(tempdir(), paste0(id, ".weights.h5"))

  history <- model |> fit(
    partial_x_train, partial_y_train,
    epochs          = EXPERIMENT_EPOCHS,
    batch_size      = BATCH_SIZE,
    validation_data = list(x_val, y_val),
    callbacks       = list(callback_model_checkpoint(
      filepath          = checkpoint_path,
      monitor           = "val_accuracy",
      save_best_only    = TRUE,
      save_weights_only = TRUE
    )),
    verbose = 0
  )

  # keras3's fit() returns an R object; per-epoch values are in $metrics
  m <- lapply(history$metrics, function(v) as.numeric(unlist(v)))
  stopifnot(length(m$val_accuracy) == EXPERIMENT_EPOCHS)

  history_df <- tibble(
    id             = id,
    epoch          = seq_along(m$accuracy),
    train_accuracy = m$accuracy,
    val_accuracy   = m$val_accuracy,
    train_loss     = m$loss,
    val_loss       = m$val_loss
  )
  write_csv(history_df, file.path("results", paste0("history_", id, ".csv")))

  test_last <- model |> evaluate(x_test, y_test, verbose = 0)
  model |> load_model_weights(checkpoint_path)
  test_best <- model |> evaluate(x_test, y_test, verbose = 0)

  best_epoch <- which.max(m$val_accuracy)

  summary_row <- tibble(
    id, label, group, hidden_layers, units, activation,
    loss_function, dropout_rate, l2,
    best_epoch,
    best_val_accuracy  = m$val_accuracy[best_epoch],
    last_val_accuracy  = tail(m$val_accuracy, 1),
    overfit_gap        = tail(m$accuracy, 1) - tail(m$val_accuracy, 1),
    test_accuracy_best = as.numeric(test_best[["accuracy"]]),
    test_accuracy_last = as.numeric(test_last[["accuracy"]])
  )
  stopifnot(nrow(summary_row) == 1)

  list(summary = summary_row, history = history_df)
}
```

# Running the Experiments

```{r experiment-grid}
experiment_grid <- tribble(
  ~id,                ~label,                       ~group,
  ~hidden_layers, ~units, ~activation, ~loss_function, ~dropout_rate, ~l2,
  "base_2x16",        "2x16 ReLU, BCE (baseline)",  "Baseline",
  2L, 16L, "relu", "binary_crossentropy", 0,   0,
  "depth_1x16",       "1x16 ReLU, BCE",             "Depth",
  1L, 16L, "relu", "binary_crossentropy", 0,   0,
  "depth_3x16",       "3x16 ReLU, BCE",             "Depth",
  3L, 16L, "relu", "binary_crossentropy", 0,   0,
  "width_2x8",        "2x8 ReLU, BCE",              "Width",
  2L,  8L, "relu", "binary_crossentropy", 0,   0,
  "width_2x32",       "2x32 ReLU, BCE",             "Width",
  2L, 32L, "relu", "binary_crossentropy", 0,   0,
  "width_2x64",       "2x64 ReLU, BCE",             "Width",
  2L, 64L, "relu", "binary_crossentropy", 0,   0,
  "loss_mse_2x16",    "2x16 ReLU, MSE",             "Loss",
  2L, 16L, "relu", "mse",                 0,   0,
  "act_tanh_2x16",    "2x16 tanh, BCE",             "Activation",
  2L, 16L, "tanh", "binary_crossentropy", 0,   0,
  "act_tanh_2x32",    "2x32 tanh, BCE",             "Activation",
  2L, 32L, "tanh", "binary_crossentropy", 0,   0,
  "reg_drop_2x16",    "2x16 ReLU, dropout 0.5",     "Regularization",
  2L, 16L, "relu", "binary_crossentropy", 0.5, 0,
  "reg_l2_2x16",      "2x16 ReLU, L2 0.001",        "Regularization",
  2L, 16L, "relu", "binary_crossentropy", 0,   0.001,
  "reg_drop_2x32",    "2x32 ReLU, dropout 0.5",     "Regularization",
  2L, 32L, "relu", "binary_crossentropy", 0.5, 0,
  "reg_drop_2x64",    "2x64 ReLU, dropout 0.5",     "Regularization",
  2L, 64L, "relu", "binary_crossentropy", 0.5, 0,
  "reg_drop_l2_2x64", "2x64 ReLU, dropout 0.5 + L2", "Regularization",
  2L, 64L, "relu", "binary_crossentropy", 0.5, 0.001
)

runs <- lapply(seq_len(nrow(experiment_grid)), function(i) {
  do.call(run_experiment, as.list(experiment_grid[i, ]))
})

results_summary <- bind_rows(lapply(runs, `[[`, "summary"))
histories       <- bind_rows(lapply(runs, `[[`, "history")) |>
  left_join(select(results_summary, id, label), by = "id")

write_csv(results_summary, "results/results_summary.csv")
write_csv(histories, "results/all_histories.csv")

cat("Experiments completed:", nrow(results_summary), "of",
    nrow(experiment_grid), "\n")
```

```{r helpers, include = FALSE}
pct <- function(x, acc = 0.01) percent(x, accuracy = acc)

# Comparison table for a set of experiment ids, in the order given
results_table <- function(ids, caption) {
  results_summary |>
    filter(id %in% ids) |>
    arrange(match(id, ids)) |>
    transmute(
      Model           = label,
      `Best ep.`      = best_epoch,
      `Val. (best)`   = pct(best_val_accuracy),
      `Test (best)`   = pct(test_accuracy_best),
      `Test (ep. 20)` = pct(test_accuracy_last),
      `Gap (ep. 20)`  = pct(overfit_gap)
    ) |>
    knitr::kable(caption = caption, booktabs = TRUE, linesep = "",
                 align = "lrrrrr")
}

# Training/validation curves for a set of experiment ids
plot_curves <- function(ids, title) {
  histories |>
    filter(id %in% ids) |>
    mutate(label = factor(label, levels = results_summary$label[
      match(ids, results_summary$id)])) |>
    pivot_longer(c(train_accuracy, val_accuracy, train_loss, val_loss),
                 names_to = c("split", "metric"), names_sep = "_") |>
    mutate(panel = factor(
      paste(ifelse(split == "train", "Training", "Validation"),
            ifelse(metric == "accuracy", "accuracy", "loss")),
      levels = c("Training accuracy", "Validation accuracy",
                 "Training loss", "Validation loss"))) |>
    ggplot(aes(epoch, value, colour = label)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~ panel, ncol = 2, scales = "free_y") +
    scale_colour_brewer(palette = "Dark2") +
    labs(title = title, x = "Epoch", y = NULL, colour = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom") +
    guides(colour = guide_legend(ncol = 2))
}

delta_pp <- function(x) sprintf("%+.2f pp", 100 * x)
```

The tables in the next five sections use these columns:

* **Best ep.** and **Val. (best)**: the epoch with the highest validation
  accuracy, and that accuracy.
* **Test (best)**: test accuracy using the weights from the best epoch.
* **Test (ep. 20)**: test accuracy after all 20 epochs, which shows the cost
  of overtraining.
* **Gap (ep. 20)**: training accuracy minus validation accuracy at epoch 20.
  Larger values mean more overfitting.

# Number of Hidden Layers (Question 1)

```{r depth-table}
depth_ids <- c("depth_1x16", "base_2x16", "depth_3x16")
results_table(depth_ids, "Effect of the number of hidden layers (16 units)")
```

```{r depth-plot, fig.cap = "Training and validation curves for 1, 2 and 3 hidden layers."}
plot_curves(depth_ids, "Hidden-layer depth")
```

# Number of Hidden Units (Question 2)

```{r units-table}
units_ids <- c("width_2x8", "base_2x16", "width_2x32", "width_2x64")
results_table(units_ids, "Effect of the number of units per layer (2 layers)")
```

```{r units-plot, fig.cap = "Training and validation curves for 8, 16, 32 and 64 units per layer."}
plot_curves(units_ids, "Hidden units per layer")
```

# MSE versus Binary Crossentropy (Question 3)

```{r loss-table}
loss_ids <- c("base_2x16", "loss_mse_2x16")
results_table(loss_ids, "Binary crossentropy versus mean squared error")
```

```{r loss-plot, fig.cap = "Training and validation curves for BCE and MSE. The loss panels are on different scales, so compare accuracy rather than loss values."}
plot_curves(loss_ids, "Loss function")
```

# tanh versus ReLU (Question 4)

```{r activation-table}
activation_ids <- c("base_2x16", "act_tanh_2x16", "width_2x32", "act_tanh_2x32")
results_table(activation_ids, "ReLU versus tanh at 16 and 32 units")
```

```{r activation-plot, fig.cap = "Training and validation curves for ReLU and tanh."}
plot_curves(activation_ids, "Activation function")
```

# Regularization to Improve Validation (Question 5)

Dropout randomly sets 50% of hidden activations to zero during training, and
L2 regularization penalizes large weights. Both limit how closely the network
can memorize the training reviews.

```{r reg-table}
reg_ids <- c("base_2x16", "reg_drop_2x16", "reg_l2_2x16",
             "reg_drop_2x32", "width_2x64", "reg_drop_2x64",
             "reg_drop_l2_2x64")
results_table(reg_ids, "Effect of dropout and L2 regularization")
```

```{r reg-plot, fig.cap = "Training and validation curves with and without regularization.", fig.height = 5.5}
plot_curves(reg_ids, "Regularization")
```

# Summary of All Experiments

```{r summary-table}
results_summary |>
  arrange(desc(best_val_accuracy)) |>
  transmute(
    Rank                = row_number(),
    Model               = label,
    Group               = group,
    `Best epoch`        = best_epoch,
    `Val. acc. (best)`  = pct(best_val_accuracy),
    `Test acc. (best)`  = pct(test_accuracy_best)
  ) |>
  knitr::kable(caption = "All experiments ranked by best validation accuracy",
               booktabs = TRUE, linesep = "", align = "rllrrr")
```

```{r summary-plot, fig.cap = "Best validation accuracy and matching test accuracy for every model. The dashed line marks the baseline's validation accuracy.", fig.height = 6}
baseline_val <- results_summary$best_val_accuracy[results_summary$id == "base_2x16"]

results_summary |>
  mutate(label = reorder(label, best_val_accuracy)) |>
  pivot_longer(c(best_val_accuracy, test_accuracy_best),
               names_to = "metric", values_to = "accuracy") |>
  mutate(metric = ifelse(metric == "best_val_accuracy",
                         "Validation (best epoch)", "Test (best-epoch weights)")) |>
  ggplot(aes(accuracy, label)) +
  geom_vline(xintercept = baseline_val, linetype = "dashed", colour = "grey50") +
  geom_line(aes(group = label), colour = "grey75") +
  geom_point(aes(colour = group, shape = metric), size = 3) +
  scale_x_continuous(labels = percent_format(accuracy = 0.1)) +
  scale_shape_manual(values = c(17, 16)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(title = "IMDB hyperparameter experiments",
       x = "Accuracy", y = NULL, colour = "Group", shape = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", legend.box = "vertical")
```

# Final Model

The configuration with the highest validation accuracy is retrained on all
25,000 training reviews for the number of epochs at which it peaked, then
evaluated once on the test set.

```{r final-model}
selected <- results_summary |>
  slice_max(best_val_accuracy, n = 1, with_ties = FALSE)
baseline <- results_summary |> filter(id == "base_2x16")

set_random_seed(SEED)
final_model <- build_imdb_model(
  hidden_layers = selected$hidden_layers,
  units         = selected$units,
  activation    = selected$activation,
  loss_function = selected$loss_function,
  dropout_rate  = selected$dropout_rate,
  l2            = selected$l2
)

final_history <- final_model |> fit(
  x_train_full, y_train_full,
  epochs     = selected$best_epoch,
  batch_size = BATCH_SIZE,
  verbose    = 0
)

final_test     <- final_model |> evaluate(x_test, y_test, verbose = 0)
final_test_acc <- as.numeric(final_test[["accuracy"]])

final_results <- tibble(
  Run                     = c("Selected model, final",
                              "Baseline, experiment run"),
  Model                   = c(selected$label, baseline$label),
  `Training epochs`       = c(selected$best_epoch, baseline$best_epoch),
  `Val. acc. (best)`      = c(selected$best_val_accuracy,
                              baseline$best_val_accuracy),
  `Test acc.`             = c(final_test_acc, baseline$test_accuracy_best)
)
write_csv(final_results, "results/final_model_results.csv")

final_results |>
  mutate(across(c(`Val. acc. (best)`, `Test acc.`), pct)) |>
  knitr::kable(
    caption = "Final model (retrained on all 25,000 reviews) versus baseline",
    booktabs = TRUE, align = "llrrr")
```

The baseline row shows its test accuracy from the experiment run (trained on
15,000 reviews, best-epoch weights) for reference.

# Conclusions

```{r conclusions, echo = FALSE, results = "asis"}
get <- function(i) results_summary[results_summary$id == i, ]
d   <- function(i) get(i)$best_val_accuracy - baseline$best_val_accuracy

verdict <- function(x) {
  if (abs(x) < 0.005) "essentially no change (within run-to-run noise)"
  else if (x > 0) "an improvement" else "a drop"
}

depth_best <- results_summary |> filter(id %in% depth_ids) |>
  slice_max(best_val_accuracy, n = 1, with_ties = FALSE)
units_best <- results_summary |> filter(id %in% units_ids) |>
  slice_max(best_val_accuracy, n = 1, with_ties = FALSE)
unreg_best <- results_summary |> filter(dropout_rate == 0, l2 == 0) |>
  slice_max(best_val_accuracy, n = 1, with_ties = FALSE)
reg_best   <- results_summary |> filter(dropout_rate > 0 | l2 > 0) |>
  slice_max(best_val_accuracy, n = 1, with_ties = FALSE)

unreg_models <- results_summary |> filter(dropout_rate == 0, l2 == 0)
delta_range  <- sprintf("%.1f-percentage-point",
                        100 * diff(range(unreg_models$best_val_accuracy)))

cat(
  "* **Hidden layers.** Relative to the two-layer baseline (",
  pct(baseline$best_val_accuracy), " validation), one layer gave ",
  delta_pp(d("depth_1x16")), " (", verdict(d("depth_1x16")), ") and three ",
  "layers gave ", delta_pp(d("depth_3x16")), " (",
  verdict(d("depth_3x16")), "). The best depth was **", depth_best$label,
  "**. The three-layer network peaked at epoch ",
  get("depth_3x16")$best_epoch, " versus epoch ",
  get("depth_1x16")$best_epoch, " for one layer",
  if (depth_best$id == "depth_3x16") "." else
    ", so the extra capacity mainly speeds up overfitting.",
  "\n\n",

  "* **Hidden units.** The best width was **", units_best$label, "** (",
  pct(units_best$best_val_accuracy), "). The epoch-20 overfit gap was ",
  pct(get("width_2x8")$overfit_gap), " with 8 units and ",
  pct(get("width_2x64")$overfit_gap), " with 64 units",
  if (get("width_2x64")$overfit_gap > get("width_2x8")$overfit_gap)
    ", so wider layers memorize the training set more." else ".",
  "\n\n",

  "* **Loss function.** MSE gave ", delta_pp(d("loss_mse_2x16")),
  " validation accuracy versus binary crossentropy (",
  verdict(d("loss_mse_2x16")), "). Binary crossentropy is the natural loss ",
  "for a sigmoid output because it penalizes confident wrong predictions ",
  "much more heavily.\n\n",

  "* **Activation.** tanh gave ", delta_pp(d("act_tanh_2x16")),
  " at 16 units and ",
  delta_pp(get("act_tanh_2x32")$best_val_accuracy -
           get("width_2x32")$best_val_accuracy),
  " at 32 units, relative to ReLU at the same width.\n\n",

  "* **Regularization.** The best regularized model (**", reg_best$label,
  "**, ", pct(reg_best$best_val_accuracy), ") compares with ",
  pct(unreg_best$best_val_accuracy), " for the best unregularized model (",
  unreg_best$label, "), ",
  delta_pp(reg_best$best_val_accuracy - unreg_best$best_val_accuracy),
  ". For the 64-unit network, dropout changed the epoch-20 overfit gap ",
  "from ", pct(get("width_2x64")$overfit_gap), " to ",
  pct(get("reg_drop_2x64")$overfit_gap), ", and its test accuracy after 20 ",
  "epochs was ", pct(get("reg_drop_2x64")$test_accuracy_last),
  " versus ", pct(get("width_2x64")$test_accuracy_last),
  " without dropout.\n\n",

  "* **Final model.** **", selected$label, "** was selected on validation ",
  "accuracy (", pct(selected$best_val_accuracy), "). Retrained on all ",
  "25,000 reviews for ", selected$best_epoch, " epoch(s), it reached **",
  pct(final_test_acc), "** test accuracy, compared with ",
  pct(baseline$test_accuracy_best), " for the baseline.\n",
  sep = ""
)
```

**Overall story.** The curves show that the main challenge on this task is
overfitting rather than a lack of capacity: the unregularized models reach
their best validation accuracy early (between epochs
`r min(unreg_models$best_epoch)` and `r max(unreg_models$best_epoch)`) and
then decline while training accuracy keeps rising toward 100%. Across the
architecture changes in Questions 1 to 4, best validation accuracy stayed
within a `r delta_range` range. The two most useful tools are therefore
stopping at the best epoch, which every model here uses for its test score,
and regularization such as dropout, which slows the collapse of validation
accuracy when a model is trained for longer than it needs.
